---
title: "Analysis of Data for Round sardines"
output:
  github: github
  html_document: default
  pdf_document: default
---
## Packages utilised
### vcfR
### readr
### ggplot2
### reshape2
### pegas
### ape  
### ade4
### adegenet
### poppr
### readxl
### readr
### devtools
### gstudio
### hierfstat
### poppr
### StAMPP
### lattice
### dplyr




```{r include=FALSE}
library(vcfR)
library(treemap)
library(readr)
require(devtools)
library(gstudio)
library(readr)
library(ggplot2)
library(reshape2)
library(pegas)
library(ape)  
library(ade4)
library(adegenet)
library(diveRsity)
library(genetics)
library(hierfstat)
library(iterators)
library(poppr)
library(readxl)
library(readr)
library("magrittr")
library(devtools)
library(gstudio)
library("mmod")
library(readr)
library(pegas)
library(ape)  
library(ade4)
library(genetics)
library(hierfstat)
library(iterators)
library(poppr)
library(readxl)
library(adegenet)
library(pegas)
library(StAMPP)
library(lattice)
library(ggplot2)
library(ape)
library(ggmap)
library(dplyr)
library(maps)
library("devtools")
library(StAMPP)
library(lattice)
library(ape)
library(ggmap)
```

### Import data into R
```{r}
AU1 <- read.vcfR("~/Desktop/aurita/SNP.AUdp5p05FHWE2Apca.recode.vcf")
```

### convert dataset into genind objects 
```{r }
genindB <- vcfR2genind(AU1)
strata<- read.table("~/Desktop/S_A.strata.txt", header=TRUE)
strata_df <- data.frame(strata)
strata(genindB) <- strata_df
setPop(genindB) <- ~Population
```

### Test for  Population Structure
```{r}
fstat(genindB)
wc(genindB)
```

### Calculating pairwise FST values
```{r}
Fst <- pairwise.fst(genindB)
Fst
```

### calculate genetic differentiation between pairs of population using genetic distance
```{r}
GD <- genet.dist(genindB, method = "WC84")
GD
```

### Calculating WC pairwise Fst betwen all pairs of regions using heatmap
```{r}
gindF.fst.mat <- pairwise.fst(genindB, pop = strata(genindB)$Population,res.type = "matrix")
gindF.fst.mat
reg_names = c("Benin","Ghana","Mauritania","Senegal","Togo")
colnames(gindF.fst.mat)<- reg_names
rownames(gindF.fst.mat)<- reg_names

gindF.fst.mat.tri <- gindF.fst.mat
gindF.fst.mat.tri[lower.tri(gindF.fst.mat, diag=TRUE)] <- NA
melted <- melt(gindF.fst.mat, na.rm =TRUE)
par(mfrow=c(2,1))
ggplot(data = melted, aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+
  scale_fill_gradient(low = "white", high = "red", name="FST")  +
  ggtitle(expression(atop("Pairwise FST, WC (1984)", atop(italic("N = 137, L = 9,170"), ""))))+
  labs( x = "Sampling Site", y = "Sampling Site") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 6, hjust = 1),axis.text.y = element_text(size = 10)) +
  coord_fixed()

```

### Principal Component Analysis (PCA)
```{r}
X <- tab(genindB, freq = TRUE, NA.method = "mean")
pca1 <- dudi.pca(X, scale = FALSE, scannf = FALSE, nf = 3)
barplot(pca1$eig[1:20], main = "PCA eigenvalues", col = heat.colors(50))
col <- funky(9) 
s.class(pca1$li, pop(genindB),xax=1,yax=2, col=col, axesell=FALSE, cstar=0, cpoint=2, grid=FALSE)
```

### Discriminant Analysis of Principal Components(DAPC) plot
```{r}
aa.genlightB <- vcfR2genlight(AU1, n.cores=1)
locNames(aa.genlightB) <- paste(AU1@fix[,1],AU1@fix[,2],sep="_")
pop(aa.genlightB)<-substr(indNames(aa.genlightB),1,3)

dapcB <- dapc(aa.genlightB, n.pca=13, n.da=2)
scatter(dapcB,scree.da=TRUE, bg="white", posi.pca="topright", legend=FALSE,
txt.leg=paste("group", 1:5), col=c("red","blue", "green", "black", "violet"))
```

### Neighbour Joining Tree plotted with boostrap values
```{r}
set.seed(999)
genindB %>%
  genind2genpop(pop = ~Population) %>%
  aboot(cutoff = 50, quiet = TRUE, sample = 54, distance = nei.dist)
```
### structure-like plot indicating membership probability of each sample
```{r}
dapcB.results <- as.data.frame(dapcB$posterior)
dapcB.results$pop <- pop(genindB)
dapcB.results$indNames <- rownames(dapcB.results)
library(reshape2)
dapcB.results <- melt(dapcB.results)
colnames(dapcB.results) <- c("Original_Pop","Sample","Assigned_Pop","Posterior_membership_probability")

p <- ggplot(dapcB.results, aes(x=Sample,y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity') 
p <- p + facet_grid(~Original_Pop, scales = "free")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5))
p
```

```{r}
# calculate mean per population
grouped_data <- group_by(dapcB.results, Original_Pop, Assigned_Pop)
data_means <- summarise(grouped_data, mean=mean(Posterior_membership_probability))
# plot means for each original pop colored by assigned pop
pieB <- ggplot(data_means, aes(x=Original_Pop,y=mean, fill=Assigned_Pop))
pieB <- pieB + geom_bar(stat='identity') + coord_polar("y",start=0)
pieB <- pieB + facet_grid(~Original_Pop, scales = "free") + theme(axis.text=element_blank(), axis.ticks=element_blank(), panel.grid = element_blank(), strip.background = element_blank())
pieB
```
